Apartment Evaluations Have Been Beneficial to the City of Toronto

### 2022-02-07 outputs/paper/paper.Rmd
accesory work

sapply(data, class)
data[,1:5] <- sapply(data[,1:5], as.numeric)
data[,7:7] <- sapply(data[,7:7], as.numeric)
data[,10:11] <- sapply(data[,10:11], as.numeric)
data[,13:13] <- sapply(data[,13:13], as.numeric)
data[,14:35] <- sapply(data[,14:35], as.numeric)
data <- data %>% 
  filter(PROPERTY_TYPE == "PRIVATE")

mean_data <- data %>%
  group_by(WARDNAME) %>%
  mutate(mean_scores = mean(SCORE))

@@

>>>>

#changing data types to numeric
sapply(data, class)
data[,1:5] <- sapply(data[,1:5], as.numeric)
data[,7:7] <- sapply(data[,7:7], as.numeric)
data[,10:11] <- sapply(data[,10:11], as.numeric)
data[,13:13] <- sapply(data[,13:13], as.numeric)
data[,14:35] <- sapply(data[,14:35], as.numeric)
data <- data %>% 
  filter(PROPERTY_TYPE == "PRIVATE")

#adding a mean data column for each ward
mean_data <- data %>%
  group_by(WARDNAME) %>%
  mutate(mean_scores = mean(SCORE))

@@

# Conclusion

Whenever the government introduces a new program or policy, I belive it has higher chances of failing than success. Especially if its something new that people don't expect and take time getting accustomed to. The RentSafeTO program according to me turned out to be a successfull one. We can clearly see a growth in the average score every year, albeit taking a bit of a hit due the global coronavirus pandemic in the last 2 years. This growth means that the living conditions have gone from good to better, and more people are inclined to get a place in the city. After things normalize from the pandemic, continuing this program will make sure building owners and landlords abide to it and make sure to maintain a safe and healthy place for poeple to live in. I hope the living conditions continue to get better through the help of this program, even if its just a small contribution.
